Hierarchical ARIMA

### 2020-08-19 KB_modeling.Rmd
changed lag from meeting

dat %>%
  filter(team %in% example_teams) %>%
  ggplot(aes(x = date, y = ghits_e2, color = team)) +
  geom_line()
```

@@

```{r}
final_model <- 
  dat  %>%
  lm(ghits_e2 ~ phase + is_playoffs:playoffs + lag(ghits_e2, 1), data = .) ## needs to be AR model instead, monthly
  # lm(ghits_e2 ~ phase + is_playoffs:playoffs, data = .)

@@

dat %>%
  filter(team %in% example_teams) %>%
  ggplot(aes(x = date, y = ghits_e3, color = team)) +
  geom_line()
```

>>>>

dat %>%
  filter(team %in% example_teams) %>%
  ggplot(aes(x = date, y = ghits_e2, color = team)) +
  geom_line() +
```

@@

```{r}
final_model <- 
  dat  %>%
  lm(ghits_e2 ~ phase + is_playoffs:playoffs + lag(ghits_e2, 12), data = .) ## needs to be AR model instead, monthly
  # lm(ghits_e2 ~ phase + is_playoffs:playoffs, data = .)

@@

dat %>%
  filter(team == "Arizona Diamondbacks") %>%
  # filter(team %in% example_teams) %>%
  ggplot(aes(x = date, y = ghits_e3, color = team)) +
  geom_line()
```
